The Two Dualities of Computation: Negative and Fractional Types

### 2012-03-08 rational.tex
sat

Consider the circuit below that has no observable output -- i.e. for
all inputs it is annihilating. This happens because it constructs a
boolean and its dual, negates one of them and attempts to collapse
them.
\begin{center}
\scalebox{1.5}{
  \includegraphics{diagrams/not_trace.pdf}
}
\end{center}

@@

>>>>

Consider the circuit below that has no observable output -- i.e. for
all inputs it is annihilating. This happens because it constructs a
boolean and its dual, negates one of them and attempts to collapse
them.
\begin{center}
\scalebox{1.2}{
  \includegraphics{diagrams/not_trace.pdf}
}
\end{center}

@@

The final detail we have to be concerned with is the handling of the
heap and garbage of {{f}}. Any boolean expression {{bool^n -> bool}}
can be compiled into the isomorphism {{f:bool^h*bool^n<->bool^g*bool}}
where the extra bits {{bool^h}} and {{bool^g}} are the heap and
garbage. Constructing such an isomorphism has been detailed before
\cite{Toffoli:1980,infeffects}.  However the computation of {{f}} is
meaningful {{iff}} the heap {{bool^h}} is initialized appropriately. We
can ensure that the heap has the appropriate initial value by checking
the heap and negating a second control wire, if the values do not
match.

\begin{center}
\scalebox{1.5}{
  \includegraphics{diagrams/sat2.pdf}
}
\end{center}
